Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\section{Analysis}

>>>>

\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.
